Using reference models in variable selection \vspace{.1in}

### 2019-12-18 paper/ref_approach.tex
added table with numerical values of stepwise w/ and w/out ref model
minor stylistic edit

To motivate the further discussion and experiments, we start by simple
variable selection example using body fat data by \citet{johnson1996fitting}.
We compare the projective prediction approach (\emph{projpred},
\citet{paper:projpred}) which uses a reference model, and classic
stepwise backward regression (steplm).
% \footnote{The analysis is based on \texttt{R}-notebook by Vehtari available at
%   \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.
The experiments are implemented in \texttt{R} \citep{Rcore2018}.

The target variable of interest is the amount of body fat, which is
measured by immersing a person in water tank which is a complex and
expensive procedure. Additionally, we have information about 13
variables which are anthropometric measurements (e.g., height, weight
and circumference of different body parts). The
variables are highly correlated which causes additional
challenge in the variable selection. In total, we have 251
observations. The goal is to find the model which is able to predict
the amount of body fat well while requiring least amount of
measurements for a new person.

\cite{paper:bodyfat} report results using \emph{steplm} with a significance
level of 0.157 with AIC selection \citep{akaike1974new}, fixing
abdomen and height to be always included in the model. For better
comparison we don't fix any of the variables.  The steplm approach is
carried out combining the \texttt{step} and \texttt{lm} functions in R.

@@

>>>>

To motivate the further discussion and experiments, we start by simple
variable selection example using body fat data by \citet{johnson1996fitting}.
We compare the projective prediction approach (\emph{projpred},
\citet{paper:projpred}) which uses a reference model, and classic
stepwise backward regression (\emph{steplm}).
% \footnote{The analysis is based on \texttt{R}-notebook by Vehtari available at
%   \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.
The experiments are implemented in \texttt{R} \citep{Rcore2018}.

The target variable of interest is the amount of body fat, which is
measured by immersing a person in water tank which is a complex and
expensive procedure. Additionally, we have information about 13
variables which are anthropometric measurements (e.g., height, weight
and circumference of different body parts). The
variables are highly correlated which causes additional
challenge in the variable selection. In total, we have 251
observations. The goal is to find the model which is able to predict
the amount of body fat well while requiring the least amount of
measurements for a new person.

\cite{paper:bodyfat} report results using steplm with a significance
level of 0.157 with AIC selection \citep{akaike1974new}, fixing
abdomen and height to be always included in the model. For better
comparison we don't fix any of the variables.  The steplm approach is
carried out combining the \texttt{step} and \texttt{lm} functions in R.

@@

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{l|r|r}
%  \hline
Method & RMSE & Selected noisy \\ 
  \hline
Stepwise selection & 6.92 (0.68) & 48.1 (7.46)    \\
Reference model + Stepwise selection & 4.71 (0.45) & 25.1 (6.89)   \\
\end{tabular}
\caption{Mean and standard deviation (between brackets) values of Figure \ref{fig:bodyfat_step_refvsdata}}
\label{tab:step_refvsdata}
\end{table}
